Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield

### 2017-06-18 Tex/Paper.tex
Fixed compiling issues and added some text

\section[\label{S:M}]{Method}

- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers \\
- simulation setup PIC/quickpic OS \\

>>>>

\section[\label{S:M}]{Method}
%- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers \\
%- simulation setup PIC/quickpic OS \\

Initial beam loading studies were done using the full PIC code Osiris \cite{fonseca_osiris:_2002}. these simulations were done using a short, pre.dodulated prton drive bunch. That is, we applied a clipped cosine function to the longitudinal density profile of the proton beam, with a period matching the wavelength, $\lambda_p$, of the plasma.

\subsection[\label{S:M:Setup}]{Simulationn Setup}
